### 2018-08-05 Sections/optical_encoding_of_quantum_information.tex
TEM modes

@@

\subsection{Time-bins} \label{sec:time_bin} \index{Time-bin encoding}

>>>>

\subsubsection{Transverse electro-magnetic modes}\index{Transverse electro-magnetic modes}

Of particular interest are transverse electro-magnetic (TEM) modes, which are the two-dimensional eigenfunctions of the electro-magnetic field in the transverse direction of a light field. These are given by modulations of Hermite or Laguerre polynomials\index{Laguerre polynomials}, depending on the geometry of the medium through which the light is propagating (e.g optical fibre, free-space, wave-guides), which effectively impose boundary conditions on the electro-magnetic field.

The TEM modes are discrete, and denoted TEM$_{mn}$, where \mbox{$m,n\in \mathbb{Z}_+$}. TEM modes can be prepared and manipulated using holograms\index{Holograms}. Examples are shown in Fig.~\ref{fig:TEM_modes}.

\begin{figure*}[!htb]
\includegraphics[width=0.49\textwidth]{TEM_cylinder}
\includegraphics[width=0.49\textwidth]{TEM_rectangular}
\caption{TEM$_{mn}$ modes for cylindrical (left) and rectangular (right) mode profiles.}\index{Transverse electro-magnetic modes}\label{fig:TEM_modes}
\end{figure*}

@@

\subsubsection{Time-bins} \label{sec:time_bin} \index{Time-bin encoding}
